A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-08-25 Manuscript/PNAS-Adams-04.Rmd
vsn 4

---
Investigating macroevolutionary patterns of trait variation requires a phylogenetic perspective, because the shared ancestry among species violates the assumption of independence among trait values that is common for statistical tests [@Felsenstein1985; @HarveyPagel1991]. Accounting for this evolutionary non-independence is the purview of *phylogenetic comparative methods* (PCMs): a suite of analytical tools that condition trends in the data on the phylogenetic relatedness of observations [@Grafen1989; @GarlandIves2000; @Rohlf2001; @MartinsHansen1997; @OMeara_et_al2006;  @Beaulieu_et_al2012; @Adams2014b; @AdamsCollyer2018b]. These methods are predicated on the notion that phylogenetic signal -- the tendancy for closely related species to display similar trait values -- is present in cross-species datasets [@Felsenstein1985; @Pagel1999; @Blomberg_et_al2003]. Indeed, under numerous evolutionary models, phylogenetic signal is to be expected, as stochastic character change along the hierarchical structure of the tree of life generates trait covaration among related taxa [@Felsenstein1985; @Blomberg_et_al2003; @Revell_et_al2008].

@@

Another widely used measure of phylogenetic signal is Blomberg's *K* [@Blomberg_et_al2003], which characterizes phylogenetic signal as the ratio of observed trait variation to the amount of variation expected under Brownian motion. Blomberg's *K* can be treated as a test statistic by employing a permutation test to generate its sampling distribution [@Blomberg_et_al2003; @Adams2014a] for determining whether significant phylogenetic signal is present in data. Both $\lambda$ and *K* seem intuitive to interpret, as a value of $0$ for both corresponds to no phylogenetic signal, while a value of $1$ corresponds to the amount of phylogenetic signal expected under Brownian motion. Thus, it is tempting to regard both $\lambda$ and *K* as descriptive statistics that measure the relative strength of phylogenetic signal, providing an estimate of its magnitude for comparison.

@@

**Lambda ($\lambda$) estimates of phylogenetic signal are inaccurate.** Computer simulations reveal that for $\hat{\lambda}$, the distributional expectations of a Bernoulli variable were mostly upheld. First, the mean value of $\hat{\lambda}$ increases as $\lambda$ increases.  Second, the standard deviation of $\hat{\lambda}$ is largest at intermediate values of $\lambda$ and smallest at extreme values (Fig.1 red line), implying that the precision in estimating $\lambda$ varies across the range of input values. Third, the distributions of $\hat{\lambda}$ tend toward normal ddistributions at intermediate levels of $\lambda$ but become increasingly skewed at more extreme values of $\lambda$ (Fig. 1 blue line). For small tree sizes, it is also clear that distributions are more platykurtic at intermediate values of $\hat{\lambda}$.  However, the mean value of $\hat{\lambda}$ is negatively-biased (particularly for small tree sizes but also consistently across most of its range; Fig. 1 black line) and standard deviations of $\hat{\lambda}$ are negatively associated with tree size.  For tress of 128 species or less, $\hat{\lambda}$ are quite variable, except for cases when $\lambda$ is near or equal to $1$. Taken together these results reveal that $\hat\lambda$ is a biased statistic that inconsistently estimates  phylogenetic signal, both across tree sizes and across the range of input values. Additional simulations (Supporting Information) reveal that incorporating $\hat\lambda$ in PGLS ANOVA and regression does not adversely affect the statistical properties of PGLS parameter estimation or model evaluation (type I error, power, bias in coefficients). Thus, it is reasonable to incorporate $\hat\lambda$ in PGLS as a parameter for tuning the degree of phylogenetic signal in the dependent variables during the analysis. However, the statistical properties shown in Fig. 1 demonstrate that $\lambda$ is unsuitable as an effect size for measuring the strength of phylogenetic signal in data, and thus $\lambda$ should not be used for comparing phylogenetic signal across datasets.

@@

**Kappa (*K*) estimates of phylogenetic signal are more reliable.** Simulation results demonstrate that *K* displays better statistical properties. First, as expected, mean values of *K* increase with increasing signal ($\lambda$) irrespective of tree size, albeit non-linearly (Fig. 2 black line). Additionally, the standard deviation of *K* is consistent across tree sizes (Fig. 2 red line), and while it increases with $\lambda$, it is always less than the mean (low coefficient of variation). This finding is perhaps unsurprising, as *K* is lower-bounded by 0, and is never large for small values of $\lambda$. Importantly, *K* is normally distributed across the range of input $\lambda$; a consistent pattern regardless of tree size (Fig. 2 blue line). This result differs from those of [@Munkemuller_et_al2012], where the skewing appears to be the result of combining random values generated independently, rather than being a property of *K* itself. Overall, these findings reveal that while *K* is more reliable as an estimate of phylogenetic signal, the non-linear scaling with input signal implies that it should not be considered an effect size that measures the strength of phylogenetic signal on a common scale for comparison across datasets.

@@

![(A) Linear measures for relative body size, and regions of the body used to estimate surface area to volume (SA:V) ratios. (B) Permutation distributions of phylogenetic signal for SA:V and $\frac{BW}{SVL}$, with observed values shown as vertical bars. (C) Effect sizes ($Z_K$) for SA:V and $\frac{BW}{SVL}$, with their 95% confidence intervals (CI not standardized by $\sqrt(n)$).<span data-label="fig:f4"></span>](fig.4.png)

@@

One important advantage of the approach advocated here is that the resulting effect sizes ($Z_K$) are dimensionless, as the units of measurement cancel out during the calculation of $Z$ [@SokalRohlf2012]. Thus, $Z_K$ represents the strength of phylogenetic signal on a common and comparable scale -- measured in standard deviations -- regardless of the initial units and original scale of the phenotypic variables under investigation. This means that the strength of phylogenetic signal may be compared across datasets for continuous phenotypic traits measured in different units and scale, because those units have been standardized through their conversion to $Z_K$. For example, our approach could be utilized to determine whether the strength of phylogenetic signal (say, in response to ecological differentiation) is stronger in morphological traits (linear traits: $mm$), physiological traits (metabolic rate: $\frac{O^2}{min}$), or behavioral traits (aggression: $\frac{\#{displays}}{second}$). In fact, our empirical example provided just such a comparison, as SA:V is represented in $mm^{-1}$ while relative body size is a unitless ratio ($\frac{BW}{SVL}$). Additionally, our method  is capable of comparing the strength of phylogenetic signal in traits of different dimensionality, as estimates of phylogenetic signal using *K* have been generalized for multivariate data [$\kappa_{mult}$: see @Adams2014a]. Furthermore, tests based on $\hat{Z}_{12}$ may be utilized for comparing the strength of phylogenetic signal among datasets containing a different number of species, and even for phenotypes obtained from species in different lineages, because their phylogenetic non-independence and observed variation are taken into account in the generation of the empirical sampling distribution via permutation.

>>>>

---
Investigating macroevolutionary patterns of trait variation requires a phylogenetic perspective, because the shared ancestry of species violates the assumption of independence among trait values that is common for statistical tests [@Felsenstein1985; @HarveyPagel1991]. Accounting for this evolutionary non-independence is the purview of *phylogenetic comparative methods* (PCMs): a suite of analytical tools that condition the data by the phylogenetic relatedness of observations [@Grafen1989; @GarlandIves2000; @Rohlf2001; @MartinsHansen1997; @OMeara_et_al2006;  @Beaulieu_et_al2012; @Adams2014b; @AdamsCollyer2018b]. PCMs are predicated on the notion that phylogenetic signal -- the tendancy for closely related species to display similar trait values -- is present in cross-species datasets [@Felsenstein1985; @Pagel1999; @Blomberg_et_al2003]. Indeed, under numerous evolutionary models, phylogenetic signal is expected, as stochastic character change along the hierarchical structure of the tree of life generates trait covaration among taxa [@Felsenstein1985; @Blomberg_et_al2003; @Revell_et_al2008].

@@

Another widely used measure is Blomberg's *K* [@Blomberg_et_al2003], which characterizes phylogenetic signal as the ratio of observed trait variation to the amount of variation expected under Brownian motion. Blomberg's *K* can be treated as a test statistic by employing a permutation test to generate its sampling distribution [@Blomberg_et_al2003; @Adams2014a] for determining whether significant phylogenetic signal is present in data. Both $\lambda$ and *K* seem intuitive to interpret, as a value of $0$ for both corresponds to no phylogenetic signal, while a value of $1$ corresponds to the amount of phylogenetic signal expected under Brownian motion. Thus, it is tempting to regard both $\lambda$ and *K* as descriptive statistics that measure the relative strength of phylogenetic signal, providing an estimate of its magnitude for comparison.

@@

**Lambda ($\lambda$) estimates of phylogenetic signal are inaccurate.** Computer simulations reveal that for $\hat{\lambda}$, the distributional expectations of a Bernoulli variable were mostly upheld. First, the mean value of $\hat{\lambda}$ increases as $\lambda$ increases. Second, the precision in estimating $\lambda$ varies across the range of input values, as the standard deviation of $\hat{\lambda}$ is largest at intermediate values of $\lambda$ and smallest at extreme values (Fig.1 red line). Third, the distributions of $\hat{\lambda}$ tend toward normal distributions at intermediate levels of $\lambda$ but become increasingly skewed at more extreme values of $\lambda$ (Fig. 1 blue line). For small tree sizes, it is also clear that distributions are more platykurtic at intermediate values of $\hat{\lambda}$.  However, the mean value of $\hat{\lambda}$ is negatively-biased (particularly for small tree sizes but also consistently across most of its range; Fig. 1 black line) and standard deviations of $\hat{\lambda}$ are negatively associated with tree size.  For tress of 128 species or less, $\hat{\lambda}$ are quite variable, except for cases when $\lambda$ is near or equal to $1$. Taken together these results reveal that $\hat\lambda$ is a biased statistic that inconsistently estimates  phylogenetic signal, both across tree sizes and across the range of input values. Additional simulations (Supporting Information) reveal that incorporating $\hat\lambda$ in PGLS ANOVA and regression does not adversely affect the statistical properties of PGLS parameter estimation or model evaluation (type I error, power, bias in coefficients). Thus, it is reasonable to incorporate $\hat\lambda$ in PGLS as a parameter for tuning the degree of phylogenetic signal in the dependent variables during the analysis. However, the statistical properties shown in Fig. 1 demonstrate that $\lambda$ is unsuitable as an effect size for measuring the strength of phylogenetic signal in data, and thus $\lambda$ should not be used for comparing phylogenetic signal across datasets.

@@

**Kappa (*K*) estimates of phylogenetic signal are more reliable.** Simulation results demonstrate that *K* displays better statistical properties. First, as expected, mean values of *K* increase with increasing signal ($\lambda$) irrespective of tree size, albeit non-linearly (Fig. 2 black line). Second, the standard deviation of *K* is consistent across tree sizes (Fig. 2 red line), and while it increases with $\lambda$, it is always less than the mean (low coefficient of variation). This finding is perhaps unsurprising, as *K* is lower-bounded by 0, and is never large for small values of $\lambda$. Importantly, *K* is normally distributed across the range of input $\lambda$; a consistent pattern regardless of tree size (Fig. 2 blue line). This differs from results of [@Munkemuller_et_al2012], where the skewing appears to be due to combining random values generated independently, rather than being a property of *K* itself. Overall, these findings reveal that while *K* is more reliable as an estimate of phylogenetic signal, the non-linear scaling with input signal implies that it should not be considered an effect size that measures the strength of phylogenetic signal on a common scale for comparison across datasets.

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.4}.png}
\caption{(A) Linear measures for relative body size, and regions of the
body used to estimate surface area to volume (SA:V) ratios. (B)
Permutation distributions of phylogenetic signal for SA:V and
\(\frac{BW}{SVL}\), with observed values shown as vertical bars. (C)
Effect sizes (\(Z_K\)) for SA:V and \(\frac{BW}{SVL}\), with their 95\%
confidence intervals (CI not standardized by \(\sqrt(n)\)).{}}
\end{figure}

@@

One important advantage of the approach advocated here is that the resulting effect sizes ($Z_K$) are dimensionless, as the units of measurement cancel out during the calculation of $Z$ [@SokalRohlf2012]. Thus, $Z_K$ represents the strength of phylogenetic signal on a common and comparable scale -- measured in standard deviations -- regardless of the initial units and original scale of the phenotypic variables under investigation. This means that the strength of phylogenetic signal may be compared across datasets for continuous phenotypic traits measured in different units and scale, because those units have been standardized through their conversion to $Z_K$. For example, our approach could be utilized to determine whether the strength of phylogenetic signal (say, in response to ecological differentiation) is stronger in morphological traits (linear traits: $mm$), physiological traits (metabolic rate: $\frac{O^2}{min}$), or behavioral traits (aggression: $\frac{\#{displays}}{second}$). In fact, our empirical example provided just such a comparison, as SA:V is represented in $mm^{-1}$ while relative body size is a unitless ratio ($\frac{BW}{SVL}$). Additionally, our method  is capable of comparing the strength of phylogenetic signal in traits of different dimensionality, as estimates of phylogenetic signal using *K* have been generalized for multivariate data [$\kappa_{mult}$: see @Adams2014a]. Furthermore, tests based on $\hat{Z}_{12}$ may be utilized for comparing the strength of phylogenetic signal among datasets containing a different number of variables, and even for phenotypes obtained from species in different lineages, because their phylogenetic non-independence and observed variation are taken into account in the generation of the empirical sampling distribution via permutation.

### 2020-08-25 Manuscript/PNAS-Adams-04.tex
vsn 4

Investigating macroevolutionary patterns of trait variation requires a
phylogenetic perspective, because the shared ancestry among species
violates the assumption of independence among trait values that is
common for statistical tests (1, 2). Accounting for this evolutionary
non-independence is the purview of \emph{phylogenetic comparative
methods} (PCMs): a suite of analytical tools that condition trends in
the data on the phylogenetic relatedness of observations (3--10). These
methods are predicated on the notion that phylogenetic signal -- the
tendancy for closely related species to display similar trait values --
is present in cross-species datasets (1, 11, 12). Indeed, under numerous
evolutionary models, phylogenetic signal is to be expected, as
stochastic character change along the hierarchical structure of the tree
of life generates trait covaration among related taxa (1, 12, 13).

@@

Another widely used measure of phylogenetic signal is Blomberg's
\emph{K} (12), which characterizes phylogenetic signal as the ratio of
observed trait variation to the amount of variation expected under
Brownian motion. Blomberg's \emph{K} can be treated as a test statistic
by employing a permutation test to generate its sampling distribution
(12, 16) for determining whether significant phylogenetic signal is
present in data. Both \(\lambda\) and \emph{K} seem intuitive to
interpret, as a value of \(0\) for both corresponds to no phylogenetic
signal, while a value of \(1\) corresponds to the amount of phylogenetic
signal expected under Brownian motion. Thus, it is tempting to regard
both \(\lambda\) and \emph{K} as descriptive statistics that measure the
relative strength of phylogenetic signal, providing an estimate of its
magnitude for comparison.

@@

\textbf{Lambda (\(\lambda\)) estimates of phylogenetic signal are
inaccurate.} Computer simulations reveal that for \(\hat{\lambda}\), the
distributional expectations of a Bernoulli variable were mostly upheld.
First, the mean value of \(\hat{\lambda}\) increases as \(\lambda\)
increases. Second, the standard deviation of \(\hat{\lambda}\) is
largest at intermediate values of \(\lambda\) and smallest at extreme
values (Fig.1 red line), implying that the precision in estimating
\(\lambda\) varies across the range of input values. Third, the
distributions of \(\hat{\lambda}\) tend toward normal ddistributions at
intermediate levels of \(\lambda\) but become increasingly skewed at
more extreme values of \(\lambda\) (Fig. 1 blue line). For small tree
sizes, it is also clear that distributions are more platykurtic at
intermediate values of \(\hat{\lambda}\). However, the mean value of
\(\hat{\lambda}\) is negatively-biased (particularly for small tree
sizes but also consistently across most of its range; Fig. 1 black line)
and standard deviations of \(\hat{\lambda}\) are negatively associated
with tree size. For tress of 128 species or less, \(\hat{\lambda}\) are
quite variable, except for cases when \(\lambda\) is near or equal to
\(1\). Taken together these results reveal that \(\hat\lambda\) is a
biased statistic that inconsistently estimates phylogenetic signal, both
across tree sizes and across the range of input values. Additional
simulations (Supporting Information) reveal that incorporating
\(\hat\lambda\) in PGLS ANOVA and regression does not adversely affect
the statistical properties of PGLS parameter estimation or model
evaluation (type I error, power, bias in coefficients). Thus, it is
reasonable to incorporate \(\hat\lambda\) in PGLS as a parameter for
tuning the degree of phylogenetic signal in the dependent variables
during the analysis. However, the statistical properties shown in Fig. 1
demonstrate that \(\lambda\) is unsuitable as an effect size for
measuring the strength of phylogenetic signal in data, and thus
\(\lambda\) should not be used for comparing phylogenetic signal across
datasets.

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.2}.png}
\caption{Response of Blomberg's *K* to increasing strength of Brownian motion. ~~Gray line signifies the 1:1 line where the input value matches the estimate \(\hat K\).~~ At each input level, the dark black line represents the empirically derived expected value (mean) of
*K*, the red line is the standard deviation of
*K*, and the blue line is Shapiro Wilks statistic of
*K* (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

\textbf{Kappa (\emph{K}) estimates of phylogenetic signal are more
reliable.} Simulation results demonstrate that \emph{K} displays better
statistical properties. First, as expected, mean values of \emph{K}
increase with increasing signal (\(\lambda\)) irrespective of tree size,
albeit non-linearly (Fig. 2 black line). Additionally, the standard
deviation of \emph{K} is consistent across tree sizes (Fig. 2 red line),
and while it increases with \(\lambda\), it is always less than the mean
(low coefficient of variation). This finding is perhaps unsurprising, as
\emph{K} is lower-bounded by 0, and is never large for small values of
\(\lambda\). Importantly, \emph{K} is normally distributed across the
range of input \(\lambda\); a consistent pattern regardless of tree size
(Fig. 2 blue line). This result differs from those of (18), where the
skewing appears to be the result of combining random values generated
independently, rather than being a property of \emph{K} itself. Overall,
these findings reveal that while \emph{K} is more reliable as an
estimate of phylogenetic signal, the non-linear scaling with input
signal implies that it should not be considered an effect size that
measures the strength of phylogenetic signal on a common scale for
comparison across datasets.

@@

\textbackslash begin\{figure\} \centering
\includegraphics[width=8.25cm]{{fig.4}.png}

\textbackslash caption\{ (A) Linear measures for relative body size, and
regions of the body used to estimate surface area to volume (SA:V)
ratios. (B) Permutation distributions of phylogenetic signal for SA:V
and \(\frac{BW}{SVL}\), with observed values shown as vertical bars. (C)
Effect sizes (\(Z_K\)) for SA:V and \(\frac{BW}{SVL}\), with their 95\%
confidence intervals (CI not standardized by \(\sqrt(n)\)). \}

\textbackslash end\{figure\}

@@

One important advantage of the approach advocated here is that the
resulting effect sizes (\(Z_K\)) are dimensionless, as the units of
measurement cancel out during the calculation of \(Z\) (45). Thus,
\(Z_K\) represents the strength of phylogenetic signal on a common and
comparable scale -- measured in standard deviations -- regardless of the
initial units and original scale of the phenotypic variables under
investigation. This means that the strength of phylogenetic signal may
be compared across datasets for continuous phenotypic traits measured in
different units and scale, because those units have been standardized
through their conversion to \(Z_K\). For example, our approach could be
utilized to determine whether the strength of phylogenetic signal (say,
in response to ecological differentiation) is stronger in morphological
traits (linear traits: \(mm\)), physiological traits (metabolic rate:
\(\frac{O^2}{min}\)), or behavioral traits (aggression:
\(\frac{\#{displays}}{second}\)). In fact, our empirical example
provided just such a comparison, as SA:V is represented in \(mm^{-1}\)
while relative body size is a unitless ratio (\(\frac{BW}{SVL}\)).
Additionally, our method is capable of comparing the strength of
phylogenetic signal in traits of different dimensionality, as estimates
of phylogenetic signal using \emph{K} have been generalized for
multivariate data (16). Furthermore, tests based on \(\hat{Z}_{12}\) may
be utilized for comparing the strength of phylogenetic signal among
datasets containing a different number of species, and even for
phenotypes obtained from species in different lineages, because their
phylogenetic non-independence and observed variation are taken into
account in the generation of the empirical sampling distribution via
permutation.

>>>>

Investigating macroevolutionary patterns of trait variation requires a
phylogenetic perspective, because the shared ancestry of species
violates the assumption of independence among trait values that is
common for statistical tests (1, 2). Accounting for this evolutionary
non-independence is the purview of \emph{phylogenetic comparative
methods} (PCMs): a suite of analytical tools that condition the data by
the phylogenetic relatedness of observations (3--10). PCMs are
predicated on the notion that phylogenetic signal -- the tendancy for
closely related species to display similar trait values -- is present in
cross-species datasets (1, 11, 12). Indeed, under numerous evolutionary
models, phylogenetic signal is expected, as stochastic character change
along the hierarchical structure of the tree of life generates trait
covaration among taxa (1, 12, 13).

@@

Another widely used measure is Blomberg's \emph{K} (12), which
characterizes phylogenetic signal as the ratio of observed trait
variation to the amount of variation expected under Brownian motion.
Blomberg's \emph{K} can be treated as a test statistic by employing a
permutation test to generate its sampling distribution (12, 16) for
determining whether significant phylogenetic signal is present in data.
Both \(\lambda\) and \emph{K} seem intuitive to interpret, as a value of
\(0\) for both corresponds to no phylogenetic signal, while a value of
\(1\) corresponds to the amount of phylogenetic signal expected under
Brownian motion. Thus, it is tempting to regard both \(\lambda\) and
\emph{K} as descriptive statistics that measure the relative strength of
phylogenetic signal, providing an estimate of its magnitude for
comparison.

@@

\textbf{Lambda (\(\lambda\)) estimates of phylogenetic signal are
inaccurate.} Computer simulations reveal that for \(\hat{\lambda}\), the
distributional expectations of a Bernoulli variable were mostly upheld.
First, the mean value of \(\hat{\lambda}\) increases as \(\lambda\)
increases. Second, the precision in estimating \(\lambda\) varies across
the range of input values, as the standard deviation of
\(\hat{\lambda}\) is largest at intermediate values of \(\lambda\) and
smallest at extreme values (Fig.1 red line). Third, the distributions of
\(\hat{\lambda}\) tend toward normal distributions at intermediate
levels of \(\lambda\) but become increasingly skewed at more extreme
values of \(\lambda\) (Fig. 1 blue line). For small tree sizes, it is
also clear that distributions are more platykurtic at intermediate
values of \(\hat{\lambda}\). However, the mean value of
\(\hat{\lambda}\) is negatively-biased (particularly for small tree
sizes but also consistently across most of its range; Fig. 1 black line)
and standard deviations of \(\hat{\lambda}\) are negatively associated
with tree size. For tress of 128 species or less, \(\hat{\lambda}\) are
quite variable, except for cases when \(\lambda\) is near or equal to
\(1\). Taken together these results reveal that \(\hat\lambda\) is a
biased statistic that inconsistently estimates phylogenetic signal, both
across tree sizes and across the range of input values. Additional
simulations (Supporting Information) reveal that incorporating
\(\hat\lambda\) in PGLS ANOVA and regression does not adversely affect
the statistical properties of PGLS parameter estimation or model
evaluation (type I error, power, bias in coefficients). Thus, it is
reasonable to incorporate \(\hat\lambda\) in PGLS as a parameter for
tuning the degree of phylogenetic signal in the dependent variables
during the analysis. However, the statistical properties shown in Fig. 1
demonstrate that \(\lambda\) is unsuitable as an effect size for
measuring the strength of phylogenetic signal in data, and thus
\(\lambda\) should not be used for comparing phylogenetic signal across
datasets.

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.2}.png}
\caption{Response of Blomberg's *K* to increasing strength of Brownian motion.  At each input level, the black line represents the empirically derived expected value (mean) of
*K*, the red line is the standard deviation of
*K*, and the blue line is Shapiro Wilks statistic of
*K* (\(W=1.0\) signifies normality, \(W< 1.0\) represent
skewed distributions).{}}
\end{figure}

\textbf{Kappa (\emph{K}) estimates of phylogenetic signal are more
reliable.} Simulation results demonstrate that \emph{K} displays better
statistical properties. First, as expected, mean values of \emph{K}
increase with increasing signal (\(\lambda\)) irrespective of tree size,
albeit non-linearly (Fig. 2 black line). Second, the standard deviation
of \emph{K} is consistent across tree sizes (Fig. 2 red line), and while
it increases with \(\lambda\), it is always less than the mean (low
coefficient of variation). This finding is perhaps unsurprising, as
\emph{K} is lower-bounded by 0, and is never large for small values of
\(\lambda\). Importantly, \emph{K} is normally distributed across the
range of input \(\lambda\); a consistent pattern regardless of tree size
(Fig. 2 blue line). This differs from results of (18), where the skewing
appears to be due to combining random values generated independently,
rather than being a property of \emph{K} itself. Overall, these findings
reveal that while \emph{K} is more reliable as an estimate of
phylogenetic signal, the non-linear scaling with input signal implies
that it should not be considered an effect size that measures the
strength of phylogenetic signal on a common scale for comparison across
datasets.

@@

\begin{figure}
\centering
\includegraphics[width=8.25cm]{{fig.4}.png}
\caption{(A) Linear measures for relative body size, and regions of the
body used to estimate surface area to volume (SA:V) ratios. (B)
Permutation distributions of phylogenetic signal for SA:V and
\(\frac{BW}{SVL}\), with observed values shown as vertical bars. (C)
Effect sizes (\(Z_K\)) for SA:V and \(\frac{BW}{SVL}\), with their 95\%
confidence intervals (CI not standardized by \(\sqrt(n)\)).{}}
\end{figure}

@@

One important advantage of the approach advocated here is that the
resulting effect sizes (\(Z_K\)) are dimensionless, as the units of
measurement cancel out during the calculation of \(Z\) (45). Thus,
\(Z_K\) represents the strength of phylogenetic signal on a common and
comparable scale -- measured in standard deviations -- regardless of the
initial units and original scale of the phenotypic variables under
investigation. This means that the strength of phylogenetic signal may
be compared across datasets for continuous phenotypic traits measured in
different units and scale, because those units have been standardized
through their conversion to \(Z_K\). For example, our approach could be
utilized to determine whether the strength of phylogenetic signal (say,
in response to ecological differentiation) is stronger in morphological
traits (linear traits: \(mm\)), physiological traits (metabolic rate:
\(\frac{O^2}{min}\)), or behavioral traits (aggression:
\(\frac{\#{displays}}{second}\)). In fact, our empirical example
provided just such a comparison, as SA:V is represented in \(mm^{-1}\)
while relative body size is a unitless ratio (\(\frac{BW}{SVL}\)).
Additionally, our method is capable of comparing the strength of
phylogenetic signal in traits of different dimensionality, as estimates
of phylogenetic signal using \emph{K} have been generalized for
multivariate data (16). Furthermore, tests based on \(\hat{Z}_{12}\) may
be utilized for comparing the strength of phylogenetic signal among
datasets containing a different number of variables, and even for
phenotypes obtained from species in different lineages, because their
phylogenetic non-independence and observed variation are taken into
account in the generation of the empirical sampling distribution via
permutation.
